Collaboratively Testing the Validity of Neuroscientific Models

### 2013-12-01 NeurounitFrontiers/Paper.tex
Nearly final revisions

\def\journal{NeuroInformatics}%%% write here for which journal %%%
\def\DOI{}
\def\articleType{Methods}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Richard C. Gerkin\,$^{1,*}$ and Cyrus Omar\,$^{2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA  }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Rick Gerkin}
\def\corrAddress{ISTB-1 476}
\def\corrEmail{rgerkin@asu.edu}

@@

% Section 1.
\section{Introduction}
\label{sec:introduction}
Neuroscientists construct quantitative models to coherently explain experimental observations of neurons, circuits, brain regions and behavior. 
A model can be characterized by its \textit{scope}: the set of observable quantities that it can generate predictions about, and by its \textit{validity}: the extent to which its predictions agree with available experimental  observations of those quantities.

@@

Professional software developers face similar issues \citep{omar_sciunit_2013}. 
They must understand the scope of each component of a complex software project and verify that each component achieves desired input/output behavior. 
But software developers do not verify components by simply documenting a few interesting inputs and corresponding outputs and then presenting them to other developers for one-time review leading to an archived document. 
Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and verify its implementation on an ongoing basis as it is being developed and modified \citep{beck2003}. 
Each test individually checks that a small portion of the program meets a single correctness criterion. 
For example, a unit test might verify that one function within the program correctly handles malformed inputs. 
Collectively, the test results serve as a summary of the project as it progresses through its development cycle. 
Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
This methodology is widely adopted in practice \citep{beck2003}.

@@

Each of these examples has leveraged \emph{ad hoc} infrastructure to support model validation. 
While the specific criteria used to evaluate models can vary widely between modeling domains, the underlying methodology is common and could be implemented once. 
Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} \citep{omar_sciunit_2013} (available from \url{http://sciunit.scidash.org}). 
In this paper, we will begin by detailing \textit{SciUnit}, focusing on examples from single-neuron physiology (Sec. \ref{sec:sciunit}).

@@

  goodness of fit metric: Computes p-values based on a chi-squared test statistic, and pools them using Fisher's method.
  parameters:
    inputs: list of numpy arrays containing input currents (nA)
    means, stds: lists of observed means and standard deviations, one per input
  """
  def __init__(self, inputs, means, stds):
    self.inputs, self.means, self.stds = inputs, means, stds

@@

  def _judge(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
    })
\end{python}
\vspace{-15px}
\caption{\texttt{[neuronunit.SpikeCountTest]} An example single neuron spike count test class implemented using \textit{SciUnit}. Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-10px}
\end{figure}

@@

%In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
\subsection{Implementing a Validation Test in \textit{SciUnit}}
Fig. \ref{fig:rate_test} shows how a scientist can implement spike count tests such as the one described above using \textit{SciUnit}. 
A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (constructors are named \verbx{__init__} in Python, lines 9-10). 
The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 4-7. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
For example, given observations from CA1 cells (not shown), we can instantiate a test as follows:
\begin{ipy}
  In [0]: CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
\end{ipy}
We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided. 
As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data. 
For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}). 
Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g. \verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).

@@

The remainder of the \verbx{_judge} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} that is included with \textit{SciUnit}. 
In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for scientists who may wish to examine the result in more detail later. 
In this case we save the input currents, the model outputs and the observed means and standard deviations (line 24).

@@

Figure \ref{fig:simple_model} shows how to write a simple {family} of models, \verbx{LinearModel}, that implement the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, which we will discuss below. 
Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by the scale factor and the offset of the transformation, both scalars. 
To create a \emph{particular} linear model, a modeler provides parameter values, just as with test families:
\begin{ipy}
  In [1]: CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{ipy}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
This alternative test could thus only be used for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each test development community. 
Fig. \ref{fig:rate_test} does not include a training phase. 
If training data is externally available, models that nevertheless are capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{ipy}
  In [2]: CA1_linear_model_fit = LinearModel()
  In [3]: CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{ipy}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

\subsection{Test Suites and Score Matrices}\label{sec:visualization} A collection of tests intended to be run on the same model can be put together to form a test suite.
The following test suite could be used for a simplified version of the QSNMC, as described in Sec. \ref{sec:example}:  
\begin{ipy}
  In [5]: CA1_suite = sciunit.TestSuite([CA1_overall_test, CA1_sc_test, CA1_sl_test, CA1_sv_test, 
              CA1_isi_test, CA1_imi_test])
\end{ipy}
Like a single test, a test suite is capable of judging one or more models. 
The models must possess the union of the capabilities of the tests in a suite to be fully capable of running the suite, though partial results can also be generated. 
When a model cannot take a test because of a missing capability, the \texttt{NotApplicable} score is used (e.g. point processes cannot predict subthreshold voltages). 
The result is a \emph{score matrix}, like the one diagrammed in Fig. \ref{fig:sciunit_overview}.
\begin{ipy}
  In [6]: scores = CA1_suite.judge([ARX_model, AdEx1_model, aSRM_model, PP_model])
\end{ipy}
A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.  
For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig. \ref{fig:scidash_matrix}).

@@

\section{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as those described in the previous section. 
It is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}). 
Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an IPython notebook called \textit{hippocampus\_tests}, parameterized by data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}. 
%To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).

Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and 
identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}). Statisticians and other scientists interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community. 
Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community. 
Once the testing logic has been changed, all models can be immediately evaluated against the new metrics. 
Scientists wishing to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.

@@

GitHub is an excellent platform for this kind of activity, and is becoming a widely-used tool for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.  
We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure. 
Using these common repositories, smaller groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}. 
Each research community can develop suitable quality standards and processes for merging these pull requests.

The end result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}. 
\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec. \ref{sec:visualization}. 
We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec. 2) and on the details of the bridge technologies, below.

\section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
In the examples in the previous sections, tests were provided data explicitly, and models implemented capabilities directly. 
In many fields, however, both models and data are available from existing  community resources in standardized formats. 
In this section, we will show how to use this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic. 
In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.

@@

\end{figure}
The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to make all published data on single cell neurophysiology available in a machine-readable format \citep{tripathy_neuroelectro:_2012}.  
Currently, up to 27 electrophysiological properties are available for 93 cell types, gathered from over 2000 single pieces of published data extracted from tables in published papers. 
We have made it easy to parameterize the test families in \textit{Neuron\-Unit}  using data extracted from the NeuroElectro API. 
Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
The latter is illustrated in Figure \ref{fig:neuronunit_example}, on lines 1-4. Once data has been retrieved from NeuroElectro, associated statistics (e.g. mean, standard error and sample size) can be extracted to parameterize tests (e.g. a test of spike widths on line 10). Data from NeuroElectro is can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc. \todo{write a sentence or two about its use of the NeuroLex repository}
As NeuroElectro is the only publicly curated source of such data, it represents a key resource facilitating test construction.

\subsection{Models from NeuroML and OpenSourceBrain}\label{sec:neuroml_models}
NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion. Some simulators, notably the popular NEURON package (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), can seamlessly export model specifications as NeuroML. 
Because NeuroML is an XML specification, model descriptions can be verified for correctness and queried for model properties and components. We leverage the latter facilities to expose model capabilities automatically. %NeuroML has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.

NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off them off to a supported simulator for execution. A number of popular simulators support execution of NeuroML models, including NEURON, GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}). 
\textit{NeuronUnit} provides a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel} that takes a path to a NeuroML model as a parameter.  
NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only  time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum; see Sec. \ref{sec:neurotools}). 
It can be instantiated directly or subclassed (useful when additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}). The underlying simulator can be configured (defaulting to ??\todo{What does it default to in our code??}; not shown). In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).

@@

We use NeuroTools to implement a variety of \textit{SciUnit} capabilities in \textit{NeuronUnit}. 
For example, an \verbx{AnalogSignal} object (e.g. a membrane potential time series) from NeuroTools has a threshold detection method that returns a NeuroTools \verbx{SpikeTrain} object. 
The \textit{NeuronUnit} capability \verbx{HasSpikeTrain}  requires that a method named \verbx{get_spike_train} be implemented, returning a \verbx{SpikeTrain} object. 
\verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability that all supported NeuroML models implement.
NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can overwrite these if they wish). 
This also helps scientists by directing them to a set of common utility functions and data formats that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}

>>>>

\def\journal{NeuroInformatics}%%% write here for which journal %%%
\def\DOI{}
\def\articleType{Methods}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
\def\Authors{Richard C. Gerkin\,$^{1,*}$ and Cyrus Omar\,$^{2}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA \\
The authors contributed equally. }
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Rick Gerkin}
\def\corrAddress{ISTB-1 476}
\def\corrEmail{rgerkin@asu.edu}

@@

% Section 1.
\section{Introduction}
\label{sec:introduction}
\subsection{The problem: what do models do and how well do they do it?}
Neuroscientists construct quantitative models to coherently explain experimental observations of neurons, circuits, brain regions and behavior. 
A model can be characterized by its \textit{scope}: the set of observable quantities that it can generate predictions about, and by its \textit{validity}: the extent to which its predictions agree with available experimental  observations of those quantities.

@@

\subsection{The solution: unit testing for models}
Professional software developers face similar issues \citep{omar_sciunit_2013}. 
They must understand the scope of each component of a complex software project and verify that each component achieves desired input/output behavior. 
But software developers do not verify components by simply documenting a few interesting inputs and corresponding outputs and then presenting them to other developers for one-time review leading to an archived document. 
Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and verify its implementation on an ongoing basis as it is being developed and modified \citep{beck2003}. 
Each test individually checks that a small portion of the program meets a single correctness criterion. 
For example, a unit test might verify that one function within the program correctly handles malformed inputs. 
Collectively, the test results serve as a summary of the project as it progresses through its development cycle. 
Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
This methodology is widely adopted in practice \citep{beck2003}.

@@

\subsection{The implementation: SciUnit and NeuronUnit}
Each of these examples has leveraged \emph{ad hoc} infrastructure to support model validation. 
While the specific criteria used to evaluate models can vary widely between modeling domains, the underlying methodology is common and could be implemented once. 
Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} \citep{omar_sciunit_2013} (available from \url{http://sciunit.scidash.org}). 
In this paper, we will begin by detailing \textit{SciUnit}, focusing on examples from single-neuron physiology (Sec. \ref{sec:sciunit}).

@@

  goodness of fit metric: Computes p-values based on a chi-squared test statistic, and pools them using Fisher's method.
  parameters:
    inputs: list of numpy arrays containing input currents (pA)
    means, stds: lists of observed means and standard deviations, one per input
  """
  def __init__(self, inputs, means, stds):
    self.inputs, self.means, self.stds = inputs, means, stds

@@

  def _judge(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": inputs, "counts": counts, "empirical_means": means, "empirical_stds": stds
      })
\end{python}
\vspace{-15px}
\caption{\texttt{[neuronunit.SpikeCountTest]} An example single neuron spike count test class implemented using \textit{SciUnit}. Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec. \ref{sec:neuronunit}).}
\label{fig:rate_test}
\vspace{-10px}
\end{figure}

@@

%In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
\subsection{Implementing a Validation Test in \textit{SciUnit}}
Fig. \ref{fig:rate_test} shows how a scientist can implement spike count tests such as the one described above using \textit{SciUnit}. 
A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (constructors are named \verbx{__init__} in Python, lines 9-10). 
The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 4-7. 
%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
For example, given observations from CA1 cells (not shown), we can instantiate a test as follows:
\begin{ipy}
  In [0]: CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
\end{ipy}
We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided. 
As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience. 
Test generation for a particular system of interest will then often require simply instantiating a previously-developed family with particular experimental parameters and data. 
For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}). 
Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g. \verbx{hippocampus_tests}, as shown in Figure \ref{fig:sciunit_overview}).

@@

The remainder of the \verbx{_judge} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.scores.PValue}, a subclass of \verbx{sciunit.Score} that is included with \textit{SciUnit}. 
In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for scientists who may wish to examine the result in more detail later. 
In this case we save the input currents, the model outputs and the empirical (experimental) means and standard deviations (line 24).

@@

Figure \ref{fig:simple_model} shows how to write a simple {family} of models, \verbx{LinearModel}, that implement the capability in Fig. \ref{fig:capability} as well as another capability shown in Fig. \ref{fig:training}, which we will discuss below. 
Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by the scale factor and the offset of the transformation, both scalars. 
To create a \emph{particular} linear model, a modeler provides parameter values, just as with test families:
\begin{ipy}
  In [1]: CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{ipy}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
This alternative test could thus only be used for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each test development community. 
Fig. \ref{fig:rate_test} does not include a training phase. 
If training data is externally available, models capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{ipy}
  In [2]: CA1_linear_model_fit = LinearModel()
  In [3]: CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{ipy}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

@@

\subsection{Test Suites and Score Matrices}\label{sec:visualization} A collection of tests intended to be run on the same model can be put together to form a test suite.
The following test suite could be used for a simplified version of the QSNMC, as described in sec. \ref{sec:example}:  
\begin{ipy}
  In [5]: CA1_suite = sciunit.TestSuite([CA1_overall_test, CA1_sc_test, CA1_sl_test, CA1_sv_test, 
              CA1_isi_test, CA1_imi_test])
\end{ipy}
Like a single test, a test suite is capable of judging one or more models. 
The models must possess the union of the capabilities of the tests in a suite to be fully capable of running the suite, though partial results can also be generated. 
When a model cannot take a test because of a missing capability, the \texttt{NotApplicable} score is used (e.g. point processes cannot predict subthreshold voltages). 
The result is a \emph{score matrix}, like the one diagrammed in Fig. \ref{fig:sciunit_overview}.
\begin{ipy}
  In [6]: scores = CA1_suite.judge([ARX_model, AdEx1_model, aSRM_model, PP_model])
\end{ipy}
A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.  
For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig. \ref{fig:scidash_matrix}).

@@

\section{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as those described in the previous section. 
It is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}). 
Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository called \textit{hippocampus\_tests}, containing an IPython notebook and parameterized by empirical data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}. 
%To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).

Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and 
identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}). Statisticians and other scientists interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community. 
Rather than attempting to persuade a large number of scientists that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community. 
Once the testing logic has been changed, all models can be immediately evaluated against the new metrics. 
Scientists wishing to identify statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.

@@

GitHub is an excellent platform for this kind of activity, and is becoming a widely-used tool for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.  
We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure. 
Using these common repositories, smaller groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}. 
Each research community can develop suitable quality standards and processes for merging pull requests.

The most visible result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}. 
\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec. \ref{sec:visualization}. 
We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec. 2) and on the details of the bridge technologies, below.

\section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
In the examples in the previous sections, tests were provided data explicitly, and models implemented capabilities directly. 
In many fields, however, both models and data are available from existing  community resources in standardized formats. 
In this section, we will show how to use this existing infrastructure to make 1) parameterizing tests with published data and 2) generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic. 
In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models described in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.

@@

\end{figure}
The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to make all published data on single cell neurophysiology available in a machine-readable format \citep{tripathy_neuroelectro:_2012}.  
Currently, up to 27 electrophysiological properties are available for 93 cell types, gathered from over 2000 single pieces of published data extracted from tables in published papers. 
We have made it easy to parameterize the test families in \textit{Neuron\-Unit}  using data extracted from the NeuroElectro API. 
Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
The latter is illustrated in Figure \ref{fig:neuronunit_example}, on lines 1-4. 
Once data has been retrieved from NeuroElectro, associated statistics (e.g. mean, standard error and sample size) can be extracted to parameterize tests (e.g. a test of spike widths on line 10). 
Data from NeuroElectro can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc. \todo{write a sentence or two about its use of the NeuroLex repository}
As NeuroElectro is the only public, curated source of such data, it represents a key resource facilitating test construction.

\subsection{Models from NeuroML and OpenSourceBrain}\label{sec:neuroml_models}
NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion. Some simulators, notably the popular NEURON package (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), can seamlessly export model specifications as NeuroML. 
Because NeuroML is an XML specification, model descriptions can be verified for correctness and queried for model properties and components. We are working on leveraging the latter facilities to expose model capabilities automatically. %NeuroML has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.

NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands them off to a supported simulator for execution. A number of popular simulators support execution of NeuroML models, including NEURON, GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}). 
\textit{NeuronUnit} provides a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel} that takes a path to a NeuroML model as a parameter.  
NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only time-integrable neuron models with membrane potentials (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum; see Sec. \ref{sec:neurotools}). 
It can be instantiated directly or subclassed (useful when additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}). The underlying simulator can be configured (defaulting to ??\todo{What does it default to in our code??}; not shown). In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).\todo{Migliore ref.}\todo{Should OSB models be transiently downloaded as part of the instantiation of OSBModel?}

@@

We use NeuroTools to implement a variety of \textit{SciUnit} capabilities in \textit{NeuronUnit}. 
For example, an \verbx{AnalogSignal} object (e.g. a membrane potential time series) from NeuroTools has a threshold detection method that returns a NeuroTools \verbx{SpikeTrain} object. 
The \textit{NeuronUnit} capability \verbx{HasSpikeTrain}  requires that a method named \verbx{get_spike_train} be implemented, returning a \verbx{SpikeTrain} object. 
\verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability. 
This capability is implemented by the OSBModel class that supports all current OSB models.
NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can override these if they wish). 
This also helps scientists by directing them to a set of common utility functions and data object types that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
